Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-31 paper/paper.tex
paper: Add Results and Appendix

\begin{itemize}
  \item Our method gives valid results compatible with current methods as described in Section \ref{sec:results}.
  \item As required from the beginning, it is non-supervised and non-parameterized.
  \item The model shows a great performance compared with current methods.
  \item It is able to deal with large and dense regions. As an example,
        it has succeeded characterizing Melotte 25 (Hiades) OC. This cluster is
        really large and dense, and its relative proximity makes it difficult to
        characterize. Clusterix fails characterizing this cluster. In this case,
        our method proposes at least two more non-catalogued clusters. The analysis
        of these new clusters brings out an interesting stellar dynamics in the studied
        region. It could mean that there was a recent interaction among different molecular clouds.
\end{itemize}

@@

\subsection{Evaluación 1}

\subsection{Evaluación 2 }
En la Tabla \ref{tab_1}
\begin{table}\label{tab_1}
\caption{Unidades de las propiedades magnéticas:}

\begin{tabular}{ccc}\hline\hline
Símbolo & Cantidad & Conversión\\
\hline
$\Phi$ & flujo magnético & $1$Mx $\rightarrow 10^{-8}V\cdot s$\\
... &...&...\\
\hline\hline
\end{tabular}
\end{table}

@@

Another possible change in our model would be using DBSCAN instead of KMeans
as our initial clustering algorithm. Maybe this algorithm gives us a better starting
point for the DEC model which could improve the results.

@@

>>>>

\begin{itemize}
  \item Our method gives valid results compatible with current methods as described in Section \ref{sec:results}.
  \item As required from the beginning, it is non-supervised and non-parameterized.
  \item The model shows a great performance compared with current methods.
  \item It is able to deal with large and open regions. As an example,
        it has succeeded characterizing Melotte 25 (Hiades) OC. Also,
        the relative proximity of this cluster, 45 parsec, makes it difficult to
        characterize. Clusterix fails characterizing this cluster. In this case,
        our method proposes at least two more non-catalogued clusters. The analysis
        of these new clusters brings out an interesting stellar dynamics in the studied
        region. It could mean that there was a recent interaction among different molecular clouds.
\end{itemize}

@@

We now present the results obtained after having analyzed Melotte 25.
This is the largest cluster we have studied and one of the most difficult
to characterize by its distribution and extension.

More results are available at Appendix \ref{sec:appendix}.

Melotte 25 is located at 66.725 degrees in right ascension and 15.867 degrees in
declination with a radius of 165 arcmin and composed by more than 400,000 stars.

Table \ref{tab:results_melotte_25} shows a results summary for Melotte 25.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
\hline
        \textbf{Simbad}\tablefootnote{Results have been taken from the SIMBAD astronomical database\cite{wenger2000simbad}} & 104.92 $\pm$ 0.12 & -28.00 $\pm$ 0.09 & 21.052 $\pm$ 0.065 & - \\
        Clusterix & 106.796 $\pm$ 6.229 & -24.870 $\pm$ 5.417 & 21.210 $\pm$ 1.115 & 109 \\
        K-Means & 79.936 $\pm$ 3.7 & -45.362 $\pm$ 3.8 & 20.901 $\pm$ 0.31 & 374 \\
        DEC & 104.051 $\pm$ 3.2 & -33.424 $\pm$ 2.5 & 22.072 $\pm$ 0.13 & 219 \\
        \textbf{DEC (filt.)} & 105.96 $\pm$ 3.5 & -30.00 $\pm$ 2.4 & 21.74 $\pm$ 0.07 & 175 \\
\end{tabular}
    }
    \caption{Melotte 25 results.}
    \label{tab:results_melotte_25}
  \end{center}
\end{table}

Parameters shown are proper motion in right ascension and declination, parallax
with their respective deviations and number of stars corresponding to the OC.

Figure \ref{fig:result_melotte_25_dec} shows the groups found using the DEC model.
This model labels Melotte 25 as group \emph{g5}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_pm_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_parallax_melotte_25.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_25/dec_hr_diagram_melotte_25.png}
    \end{subfigure}
  \end{subfigure}
  \caption{Melotte 25 characterization using the DEC model.
           From the left to the right: proper motion configuration
           space, parallax histogram and H-R diagram.}
  \label{fig:result_melotte_25_dec}
\end{figure}

Table \ref{tab:hyperparameters_melotte_25} shows the hyperparameters
used for the characterization.

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 9 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 25 DEC hyperparameters.}
    \label{tab:hyperparameters_melotte_25}
  \end{center}
\end{table}

@@

Another possible change in our model would be using DBSCAN instead of K-Means
as our initial clustering algorithm. Maybe this algorithm gives us a better starting
point for the DEC model which could improve the results.

@@

\appendix
\section{APPENDIX}
\label{sec:appendix}

\subsection{NGC 2516}
\label{sec:ngc2516}

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
        Clusterix & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
        K-Means & -4.344 $\pm$ 0.14 & 9.507 $\pm$ 0.19 & 2.268 $\pm$ 0.01 & 1542 \\
        DEC & -4.426 $\pm$ 0.17 & 9.952 $\pm$ 0.20 & 2.436 $\pm$ 0.01 & 1532 \\
        \textbf{DEC (filt.)} & -4.502 $\pm$ 0.14 & 10.114 $\pm$ 0.17 & 2.392 $\pm$ 0.004 & 1072 \\
      \end{tabular}
    }
    \caption{NGC 2516 results.}
    \label{tab:app_results_ngc_2516}
  \end{center}
\end{table}

Table \ref{tab:app_results_ngc_2516} shows a results summary for NGC 2516.
The top row of Figure \ref{fig:app_result_ngc_2516_clusterix_kmeans} shows
the characterization using Clusterix+TOPCAT tools while the bottom row
shows eight clusters found by K-Means.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 characterization.
           Top: Clusterix+TOPCAT. Bottom: K-Means (\emph{g3}).}
  \label{fig:app_result_ngc_2516_clusterix_kmeans}
\end{figure}

Figure \ref{fig:app_result_ngc_2516_dec} shows the groups found using the
DEC model (top row) and the DEC model filtered (bottom row).
K-Means and DEC have labeled NGC 2516 as \emph{g3}. Although in general,
groups between K-Means and DEC models may not match.
Hyperparameters used in this characterization are listed in Table
\ref{tab:app_hyperparameters_ngc_2516}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_filtered_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 characterization (labeled as \emph{g3}).
           DEC (top). DEC filtered (bottom).}
  \label{fig:app_result_ngc_2516_dec}
\end{figure}

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 8 \\
      Clustering Layer & $\left[ 50, 50, 60 \right]$ \\
      Kernel Initializer Seed & 2 \\
      Quantil Threshold & 0.15 \\
    \end{tabular}
    \caption{NGC 2516 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2516}
  \end{center}
\end{table}

\subsection{NGC 2632}
\label{sec:ngc2632}

Figure \ref{fig:app_result_ngc_2632_clusterix_kmeans} shows NGC 2632 characterized
by the validation method (first row) and the characterization made by K-Means
showing ten clusters (second row). K-Means labels NGC 2632 as \emph{g1}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 characterization using Clusterix+TOPCAT (top) and K-Means (bottom).
           K-Means identifies NGC 2632 as \emph{g1}.}
  \label{fig:app_result_ngc_2632_clusterix_kmeans}
\end{figure}

Figure \ref{fig:app_result_ngc_2632_dec} shows the groups found using
the DEC model (first row) and the DEC model filtered (second row).
Open cluster NGC 2632 is labeled as group \emph{g1}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 characterization using DEC model (top) and DEC (filtered) (bottom).
           NGC 2632 is identified as \emph{g1}.}
  \label{fig:app_result_ngc_2632_dec}
\end{figure}

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
        Clusterix & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
        K-Means & -26.352 $\pm$ 0.82 & -15.828 $\pm$ 0.76 & 5.394 $\pm$ 0.03 & 629 \\
        DEC & -20.012 $\pm$ 0.69 & -14.742 $\pm$ 0.58 & 4.686 $\pm$ 0.03 & 894 \\
        \textbf{DEC (filt.)} & -21.571 $\pm$ 0.74 & -14.234 $\pm$ 0.61 & 4.719 $\pm$ 0.03 & 714 \\
      \end{tabular}
    }
    \caption{NGC 2632 results.}
    \label{tab:app_results_ngc_2632}
  \end{center}
\end{table}

Table \ref{tab:app_results_ngc_2632} shows a results summary for NGC 2632 analysis.
While Table \ref{tab:app_hyperparameters_ngc_2632} shows the hyperparameters
used for characterizing NGC 2632 with our model.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2632}
  \end{center}
\end{table}

\subsection{NGC 2682}
\label{sec:ngc2682}

Table \ref{tab:app_results_ngc_2682} shows a results summary for NGC 2682.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & -10.9737 $\pm$ 0.0064 & -2.9396 $\pm$ 0.0063 & 1.1325 $\pm$ 0.0011 & 1194 \\
        Clusterix+TOPCAT & -10.970 $\pm$ 0.322 & -2.958 $\pm$ 0.327 & 1.142 $\pm$ 0.080 & 649 \\
        K-Means & -8.616 $\pm$ 0.15 & -3.710 $\pm$ 0.16 & 1.196 $\pm$ 0.01 & 1374 \\
        DEC & -8.926 $\pm$ 0.15 & -3.550 $\pm$ 0.15 & 1.144 $\pm$ 0.005 & 1238 \\
        \textbf{DEC (filt.)} & -9.619 $\pm$ 0.13 & -3.317 $\pm$ 0.13 & 1.140 $\pm$ 0.003 & 990 \\
      \end{tabular}
    }
    \caption{NGC 2682 results.}
    \label{tab:app_results_ngc_2682}
  \end{center}
\end{table}

Figure \ref{fig:app_result_ngc_2682_clusterix_kmeans} shows
NGC 2682 characterized using Clusterix+TOPCAT tools (top row)
and ten clusters identified by K-Means (bottom row).
The chacterization made by K-Means labels NGC 2682 as group \emph{g4}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 K-Means characterization.
           Top row corresponds to Clusterix+TOPCAT characterization,
           while bottom row shows K-Means results identifying
           NGC 2682 as cluster \emph{g4}.}
  \label{fig:app_result_ngc_2682_clusterix_kmeans}
\end{figure}

Figure \ref{fig:app_result_ngc_2682_dec} shows the groups found using
the DEC model (first row) and the DEC model filtered (second row).
The cluster of interest is the group \emph{g2}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_filtered_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 is identified as cluster \emph{g2}.
           Top row: DEC --- Bottom row: DEC (filtered)}
  \label{fig:app_result_ngc_2682_dec}
\end{figure}

Table \ref{tab:app_hyperparameters_ngc_2682} shows the
hyperparameters used for characterizing NGC 2682 with DEC method.

\begin{table}[htbp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 0 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2682 DEC hyperparameters.}
    \label{tab:app_hyperparameters_ngc_2682}
  \end{center}
\end{table}

\subsection{MELOTTE 22}
\label{sec:melotte22}

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/pm_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/parallax_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/hr_diagram_melotte_22.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/kmeans_pm_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/kmeans_parallax_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/kmeans_hr_diagram_melotte_22.png}
    \end{subfigure}
  \end{subfigure}
  \caption{Melotte 22 characterization.
           Top row: Clusterix+TOPCAT. Bottom row: K-Means.
           Melotte 22 is labeled as cluster \emph{g1}.}
  \label{fig:app_result_melotte_22_clusterix_kmeans}
\end{figure}

Figure \ref{fig:app_result_melotte_22_clusterix_kmeans} shows Melotte 22
characterized using Clusterix+TOPCAT tools (top row) and the characterization
made by K-Means (bottom row) showing nine clusters. Melotte 22 is labeled as
group \emph{g1}.

Figure \ref{fig:app_result_melotte_22_dec} shows the groups found using
DEC model (first row) and DEC model filtered (second row).
Melotte 22 is labeled as group \emph{g2} by DEC model.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/dec_pm_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/dec_parallax_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/dec_hr_diagram_melotte_22.png}
    \end{subfigure}
  \end{subfigure}
  \centering
  \begin{subfigure}{\columnwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/dec_pm_filtered_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/dec_parallax_filtered_melotte_22.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/melotte_22/dec_hr_diagram_filtered_melotte_22.png}
    \end{subfigure}
  \end{subfigure}
  \caption{Melotte 22 is identified as cluster \emph{g2}.
           Top row: DEC --- Bottom row: DEC (filtered)}
  \label{fig:app_result_melotte_22_dec}
\end{figure}

Table \ref{tab:app_results_melotte_22} shows a results summary for Melotte 22.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{Method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
        \hline
        \textbf{Simbad} & 19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
        Clusterix & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
        K-Means & 20.25 $\pm$ 0.95 & -38.01 $\pm$ 1.08 & 7.23 $\pm$ 0.06 & 1378 \\
        DEC & 23.67 $\pm$ 1.29 & -46.23 $\pm$ 1.50 & 8.04 $\pm$ 0.09 & 878 \\
        \textbf{DEC (filt.)} & 19.50 $\pm$ 0.41 & -44.23 $\pm$ 0.39 & 7.42 $\pm$ 0.005 & 438 \\
      \end{tabular}
    }
    \caption{Melotte 22 results.}
    \label{tab:app_results_melotte_22}
  \end{center}
\end{table}

While Table \ref{tab:app_hyperparameters_melotte_22} shows the hyperparameters
used for characterizing Melotte 22 with the DEC model.

\begin{table}[hbtp]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 5 \\
      Clustering Layer & $\left[ 50, 50, 200 \right]$ \\
      Kernel Initializer Seed & 11 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{Melotte 22 DEC hyperparameters.}
    \label{tab:app_hyperparameters_melotte_22}
  \end{center}
\end{table}
